WASP-4 is Accelerating Toward the Earth

### 2020-03-21 paper/ms.tex
oops. RUWE != UWE
The UWE is 1.4

But Fig A.1 of Lindegrend+2018 clarifies that this is not significant.
minor word changes

%\documentclass[12pt,twocolumn,tighten]{aastex62}
\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{WASP-4 is accelerating toward the Earth}

@@

\explain{We learned about this after submission.}
\subsection{Astrometry}

\added{
In review, it came to our attention that observations by the Gaia satellite...
%FIXME
}

@@

We fitted each model by assuming a Gaussian likelihood and sampling
over the posterior probability distributions.  
\added{The transit timing measurements, uncertainties, and provenances
are given in Table~1.}
We sampled the posterior using the algorithm proposed by
\citet{goodman_ensemble_2010} and implemented by
\citet{foreman-mackey_emcee_2013} in \texttt{emcee}.  The prior for
the quadratic model allowed the period derivative to be either
positive or negative.

@@

Due to the custom filters of the Zorro imager, and corresponding lack
of synthetic photometry, we further assumed that all sources had
blackbody spectra. While this is a simplification, we do not have
ready access to the planetary and stellar atmosphere models needed for
the consistent calculation with the \texttt{COND03} and \texttt{MESA}
models.  We adopted the effective temperatures and bolometric
luminosities from the \citet{baraffe_evolutionary_2003} and MIST
isochrones.  Using these theoretical quantities and the
empirically-measured Zorro bandpasses, we calculated absolute
magnitudes in the 562 and 832 nm Zorro bands for stellar and planetary
mass companions.  Applying the same calculation to WASP-4 itself using
the effective temperature and bolometric luminosity from
\citetalias{bouma_wasp4b_2019}, we derived the transformation from
contrast ratio to companion mass.  The resulting
limits \added{derived if we assume maximal projected separations} are
\replaced{shown}{shown with the dotted line} in Figure~\ref{fig:mass_sma}.
\added{
However, because we are observing the primary star accelerate towards
our line of sight, the companion very well be near
inferior conjunction.
We incorporate the relevant projection effects
as described in the following paragraphs.}

@@

\added{We then incorporated the speckle imaging limits in each simulated
system as follows. After fitting for the time and argument of
periastron, all the orbital parameters needed to find the projected
separation are known (we assumed uniform sensitivity as a function of
position angle, and therefore fixed the longitude of the
ascending node to zero). We calculated the projected separation using
the parametrization given by \citet{quirrenbach_2010}, which required
solving Kepler's equation for each simulated system at the time of the
imaging observation (September 28, 2019).  If a simulated companion's
mass and projected separation put it above the 5$\sigma$ contrast curve,
we assumed it would have been detected.
We multiplied
the resulting $128\times128\times512$ cubes of radial velocity and speckle
imaging probabilities, and marginalized over the systems in each grid cell to
derive a probability distribution in mass and semi-major axis.
}
\replaced{Figure~\ref{fig:mass_sma} shows the result.}
{The contours in Figure~\ref{fig:mass_sma} show the result: the companion
responsible for the acceleration has a true mass of 10-300$\,M_{\rm
Jup}$ and an orbital distance of $10$-$100\,{\rm AU}$.}
%FIXME: might need to update this text!

>>>>

\documentclass[12pt,twocolumn,tighten]{aastex62}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{February 28, 2020}
\revised{\today}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{WASP-4 is accelerating toward the Earth}

@@

@@

We fitted each model by assuming a Gaussian likelihood and sampling
over the posterior probability distributions.  
\added{The timing measurements, uncertainties, and provenances
are given in Table~1.}
We sampled the posterior using the algorithm proposed by
\citet{goodman_ensemble_2010} and implemented by
\citet{foreman-mackey_emcee_2013} in \texttt{emcee}.  The prior for
the quadratic model allowed the period derivative to be either
positive or negative.

@@

Due to the custom filters of the Zorro imager, and corresponding lack
of synthetic photometry, we further assumed that all sources had
blackbody spectra. While this is a simplification, we do not have
ready access to the planetary and stellar atmosphere models needed for
the consistent calculation with the \texttt{COND03} and \texttt{MESA}
models.  We adopted the effective temperatures and bolometric
luminosities from the \citet{baraffe_evolutionary_2003} and MIST
isochrones.  Using these theoretical quantities and the
empirically-measured Zorro bandpasses, we calculated absolute
magnitudes in the 562 and 832 nm Zorro bands for stellar and planetary
mass companions.  Applying the same calculation to WASP-4 itself using
the effective temperature and bolometric luminosity from
\citetalias{bouma_wasp4b_2019}, we derived the transformation from
contrast ratio to companion mass.  The resulting
limits \added{derived if we assume maximal projected separations} are
\replaced{shown}{shown with the dotted line} in Figure~\ref{fig:mass_sma}.
\added{
However, because the primary star is accelerating towards
our line of sight, the companion could very well be near
inferior conjunction.
Our approach for incorporating the relevant projection effects
is described in the following paragraphs.}

@@

\added{We then incorporated the speckle imaging limits in each
simulated system as follows. After fitting for the time and argument
of periastron, all the orbital parameters needed to find the projected
separation at the time of observation are known. We assumed uniform
sensitivity as a function of position angle, and therefore fixed the
longitude of the ascending node to zero. We then calculated the
projected separation using the parametrization given by
\citet{quirrenbach_2010}.  If a simulated companion's mass and
projected separation put it above the 5$\sigma$ contrast curve, we
assumed it would have been detected.  We multiplied the resulting
$128\times128\times512$ cubes of radial velocity and speckle imaging
probabilities, and marginalized over the systems in each grid cell to
derive a probability distribution in mass and semi-major axis.
}
\replaced{Figure~\ref{fig:mass_sma} shows the result.}
{The contours in Figure~\ref{fig:mass_sma} show the result: the companion
responsible for the acceleration has a true mass of 10-300$\,M_{\rm
Jup}$ and an orbital distance of $10$-$100\,{\rm AU}$.}
%FIXME: might need to update this text!
